Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2017-02-11 manuscript/ajps/reviews_response.md

Third, the discussion of TF-IDF weighting to identify boilerplate text is interesting and novel, and I would like to see it expanded further. Other weighting schemes or boilerplate adjustment mechanisms should be discussed (e.g. using word2vec embeddings to classify boilerplate language). The reason for selecting TF-IDF weights in particular should be described in more detail.

[Addressed] I both expanded the discussion of Wilkerson et al. and our approach, and also noted that dealing with boilerplate is an important open area for research in leg politics.

Fourth, I'd like a clearer justification for the choice of the NCSL classification task as a validity exercise. Relatively little detail is given in the paper about methodology that the NCSL used to build their tables and identify comparable documents, the underlying level of variation in the NCSL tables, or similar concerns.

[Addressed] Added a cite explaining what the NCSL is, as well as several references to papers that use the NCSL to identify policy-specific lists of bills/policies across states.

@@

Finally, some smaller notes:
- The discussion of SWAlign is generally good, but the description of the dynamic implementation is somewhat tough to follow.

[Addressed] I revised this to clarify.

- In Figure 1, placing the optimal alignment alongside the table is confusing, and suggests that the terms match the axes in the figure.

[FRIDO] Would you circle or bold the terms in each axis that get included in the alignment, rather than writing them to the right?

### 2017-02-11 manuscript/main.tex
finished reviewer 2

Because there are so many different possibilities, it is computationally demanding to find the optimal alignment. \citet{smith1981identification} therefore proposed a dynamic programming approach that is illustrated in Figure \ref{fig:score_matrix}. Dynamic programming refers to algorithms that divide a problem into sub-problems and store results of previous calculations for later ones. In the case of the SW algorithm, the property that makes it a dynamic problem is the fact that all the alignments of shorter sub-sequences of an optimal alignment of a sequence are themselves optimal. Intuitively, if the benefits of including a sub-sequence in an alignment outweigh the penalties from mismatches and gaps in that sub-sequence, that sub-sequence will contribute positively to longer alignments to which it is appended. To make this clearer consider the beginning of the sequences in the example above:

@@

In our first validation exercise, we consider whether high alignment scores provide a reliable signal of similar policy proposals. To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Conference of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}} The NCSL is a non-partisan organization that provides informational assistance to state legislatures, and maintains databases of state-level legislation and law \citep{rivera2014immigration}.  We collected a sample of these tables with the following procedure:

>>>>

Because there are so many different possibilities, it is computationally demanding to find the optimal alignment. \citet{smith1981identification} therefore proposed a dynamic programming approach that is illustrated in Figure \ref{fig:score_matrix}. Dynamic programming refers to algorithms that divide a problem into sub-problems and store results of previous calculations for later ones. In the case of the SW algorithm, given an existing alignment between two sequences, as more terms are considered across the two sequences, new terms will either be added or skipped. The alignment score is never improved by removing terms from the alignment. This property makes the SW algorithm a dynamic programming problem. Intuitively, if the benefits of including a sub-sequence in an alignment outweigh the penalties from mismatches and gaps in that sub-sequence, that sub-sequence will contribute positively to longer alignments to which it is appended. To make this clearer consider the beginning of the sequences in the example above:

@@

In our first validation exercise, we consider whether high alignment scores provide a reliable signal of similar policy proposals. To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Conference of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}} The NCSL is a non-partisan organization that provides informational assistance to state legislatures, and maintains databases of state-level legislation and law \citep{rivera2014immigration}.  The NCSL tables are regularly used in state politics research to identify comparable bills and policies across states \citep[see, e.g., ][]{marquez2013hispanic,witmer2014american,commins2016reappraising,ybarra2016anti, brown2013foreclosing}. We collected a sample of these tables with the following procedure:
